Proposed Solution

### 2017-01-24 CAV17/secs/learner.tex
add extra timing results

A \textit{rule} $r$, is then an implication relationship, $r = X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
Implicitly we interpret a rule to mean that if the keywords $X\cup Y$ appear in a configuration file, the predicate $p$ should hold.
The task of the learning algorithm is to transform a training set to a set of rules, weighted with \textit{support} and \textit{confidence}.
The set of rules learned from training set \trainingSet constitutes a specification, $Spec(\trainingSet)$, for a configuration file to be considered correct.

The two metrics, support and confidence, are used in association rule learning, as well as other rule based machine learning techniques~\cite{han2007frequent,langley1995applications}.
We use slightly modified definitions of of these to handle arbitrary predicates as rules.
During the learning process, each rule is assigned a support and confidence to measure the amount and quality of evidence for the rule.
%
\begin{equation}
 support(p,X,Y) = \frac{|\{C \in \trainingSet \mid X \cup Y \subseteq C\}|} {|\trainingSet|}
\end{equation}
\begin{equation}
 confidence(p,X,Y) = \frac{|\{C \in \trainingSet \mid p(X,Y) \subseteq C\}| } {support(X,Y)*|\trainingSet|}
\end{equation}

Support is the frequency that the that set of keywords in the proposed rule, $X \cup Y$, have been seen in the configuration files $C$ in the training set \trainingSet.
%Notice support does not consider the predicate itself, only how many times the predicate had the chance to be evaluated.
Confidence is the number of times the rule predicate has held true over the given keywords.
In the learning process, each class of rule is manually assigned a support and confidence threshold, $t_s$ and $t_c$ respectively, below which a rule will be rejected for lack of evidence.
The set rules that are learned and included as part of the final specification are as follows:

\begin{align*}
Spec(\trainingSet) = \{r | \ &support(p,X,Y) > t_s\ \land \\
    & confidence(p,X,Y) > t_c\ \land \\
    & X,\ Y \subset \keys\}
\end{align*}

@@

With the rules generated by the learner module, \app checks whether any entry in a target configuration file violates the learned rules and constraints.
\app parses a verification target configuration file the same way employed in the translator for learning to obtain a set of key-value pairs $C$.
Then, the checker applies the learner to build the set of relations observed in the file.
For any relation that violates a known rule, the checker will output the predicate and keyword sets associated with that rule, as well as the learned support and confidence values.
Since the tool is probabilistic, we provide the user with these values to determine if they rule must be satisfied in their application on a case-by-case basis.
For instance, the \texttt{key\_buffer} misconfiguration from Sec. \ref{ex:fine} will only be noticeable if the application experiences a heavy traffic load, so the user may choose to ignore this error if they are confident this will not be an issue.

>>>>

A \textit{rule}, $r$, is then an implication relationship, $r = X \implies p(X,Y)$, between two possibly empty sets of keywords $X,Y \subset \keys$, where $\keys$ is the set of unique keys from the training set (denoted \trainingSet) and the predicate $p$ is one of the classes of configuration errors.
Implicitly we interpret a rule to mean that if the keywords $X\cup Y$ appear in a configuration file, the predicate $p$ should hold.
The task of the learning algorithm is to transform a training set to a set of rules, weighted with \textit{support} and \textit{confidence}.
The set of rules learned from training set \trainingSet constitutes a specification for a configuration file to be considered correct.

The two metrics, support and confidence, are used in association rule learning, as well as other rule based machine learning techniques~\cite{han2007frequent,langley1995applications}.
We use slightly modified definitions of of these to handle arbitrary predicates as rules.
During the learning process, each rule is assigned a support and confidence to measure the amount and quality of evidence for the rule.
%
\begin{equation*}
 support(r) = \frac{|\{C \in \trainingSet \mid X_r \cup Y_r \subseteq C\}|} {|\trainingSet|}
\end{equation*}
\begin{equation*}
 confidence(r) = \frac{|\{C \in \trainingSet \mid p_r(X_r,Y_r) \subseteq C\}| } {support(r)*|\trainingSet|}
\end{equation*}

Support is the frequency that the that set of keywords in the proposed rule, $X \cup Y$, have been seen in the configuration files $C$ in the training set \trainingSet.
%Notice support does not consider the predicate itself, only how many times the predicate had the chance to be evaluated.
Confidence is the number of times the rule predicate has held true over the given keywords.
In the learning process, each class of rule is manually assigned a support and confidence threshold, $t_s$ and $t_c$ respectively, below which a rule will be rejected for lack of evidence.
The denote the set rules that are learned and included as part of the final specification are as follows:

\begin{align}
Learn(\trainingSet) = \{r | \ &support(r) > t_s\ \land \nonumber \\
    & confidence(r) > t_c\ \land \label{eq:learn}\\ 
    & X,\ Y \subset \keys\} \nonumber
\end{align}

@@

With the rules generated by the learner module, \app checks whether any entry in a target configuration file violates the learned rules and constraints.
\app parses a verification target configuration file with the translator from Sec.~\ref{sec:trans}  to obtain a set of key-value pairs, $\mathcal{V}$, for that file.
Then, the checker applies the learner from Eq.~\ref{eq:learn}, $Learn(\mathcal{V})$ to build the set of relations observed in the file, with the thresholds $t_s,t_c = 100\%$. 
The checker will then report the following set of errors:

\begin{align*}
Errors(\mathcal{V}) = \{ r\ |\ & X_r \cup Y_r \in \mathcal{V} \ \land \\
                               & r \in Learn(\trainingSet) \ \land \\
                               & r \notin Learn(\mathcal{V})
\end{align*}

For any relation that violates a known rule, the checker will output the predicate and keyword sets associated with that rule, as well as the learned support and confidence values.
Since this is a probabilistic approach, in our implementation \app, we provide the user with these values to determine if they rule must be satisfied in their application on a case-by-case basis.
For instance, the \texttt{key\_buffer} misconfiguration from Sec. \ref{ex:fine} will only be noticeable if the application experiences a heavy traffic load, so the user may choose to ignore this error if they are confident this will not be an issue.

### 2017-01-24 CAV17/secs/table2.tex
add extra timing results

\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize FINE GRAINED ERROR: Expected \\ ``max\_connections'' * ``sort\_buffer\_size'' $\geq$ ``key\_buffer\_size''}}
& url & 30/34 & 18/24 & 6/7 & 3/7 \\ 
& url & 23/25 & 9/25  & 8/9 & 3/9 \\  
& url & 20/23 & 14/23 & 6/7 & 5/7 \\
\hline

>>>>

\multirow{3}{*}{\parbox{\tablewidth} {\scriptsize FINE GRAINED ERROR: Expected \\ ``max\_connections'' * ``sort\_buffer\_size'' $\geq$ ``key\_buffer\_size''}}
& url & 30/34 & 18/34 & 6/7 & 3/7 \\ 
& url & 23/25 & 9/25  & 8/9 & 3/9 \\  
& url & 20/23 & 14/23 & 6/7 & 5/7 \\
\hline
